 "RepData_PeerAssessment1"
---
####check and create working directory

```{r}
if (!file.exists("projectdata")) {dir.create("projectdata")}
```
####Download file and unzip file to folder

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(fileUrl, destfile = "./projectdata/Dataset.zip", mode = "wb")
unzip<- unzip( "./projectdata/Dataset.zip", exdir= "projectdata")
```

####set working directory to folder with unzipped data
```{r}
setwd("./projectdata")
fitdata <- read.csv("activity.csv")
fitdata1<- na.omit(fitdata)
```
####daily steps
```{r}
Dailysteps<- aggregate(fitdata1[,"steps"], list(fitdata1$date), FUN =sum)
```
####Summary Statistics, #daily mean and Median steps
```{r}
summary(fitdata1)
aggregate(fitdata1[,"steps"], list(fitdata1$date), FUN=mean)
aggregate(fitdata1[,"steps"], list(fitdata1$date), FUN=median)
```
####Histogram of Daily step totals.
```{r}
names(Dailysteps) <- c("Date", "Step_tot") 
hist(Dailysteps$Step_tot, main ="Daily Steps Histogram")
```
####What is the average daily activity pattern
```{r}
interval.steps <- aggregate(steps ~ interval, data = fitdata1, FUN = mean)
plot(interval.steps, type = "l")
interval.steps[max(interval.steps$steps),]
```
####Total  of missing Values
```{r}
sum(is.na(fitdata))
```
####Replace missing(N/A's) values
```{r}
fitdata$steps[is.na(fitdata$steps)]<-0
```
####Plot New Hist without missing data
```{r}
Dailysteps_all<- aggregate(fitdata[,"steps"], list(fitdata$date), FUN =sum)
names(Dailysteps_all) <- c("Date", "Step.tot") 
hist(Dailysteps_all$Step.tot, main ="Daily Steps Histogram")
```
####Summary Statistics, daily mean and median steps,
```{r}
summary(fitdata)
aggregate(fitdata[,"steps"], list(fitdata$date), FUN=mean)
aggregate(fitdata[,"steps"], list(fitdata$date), FUN=median)







